WHOOMP! (There It Is) \\ Rapid Bayesian position reconstruction for gravitational\nobreakdashes-wave transients

### 2014-05-29 ms.tex
Add value of autocorrelation function and derivatives at t=0
Clean up signal model

Assuming circular orbits and no spin precession, we can write the \ac{GW} signal in each detector as a linear combination of two basis waveforms $h_0$ and $h_{\pi/2}$. For nonprecessing systems, $h = h_0$ and $h_{\pi/2}$ are approximately ``in quadrature'' in the same sense as the sine and cosine functions, being nearly orthogonal and out of phase by ${\pi/2}$ at all frequencies. In other words, $h_{\pi/2}(\omega) = i h_0(\omega)$ for all $\omega$. This linear combination isolates all dependence on the extrinsic parameters $\boldsymbol\theta_\mathrm{ex}$ into the coefficients and all dependence on the intrinsic parameters $\boldsymbol\theta_\mathrm{in}$ into the basis waveform,
%
\begin{eqnarray}\label{eq:full-signal-model}
	\fl h_i(\omega; \boldsymbol\theta) &=& e^{-i\omega t_\oplus}\frac{D_{1,i}}{D_\mathrm{L}}
	\left(\begin{array}{cc}
		F_{+,i}(\alpha, \delta, t_\oplus) \\
		F_{\times,i}(\alpha, \delta, t_\oplus)
	\end{array}\right)^\intercal
	\left(\begin{array}{cc}
		\cos{2\psi} & -\sin{2\psi} \\
		\sin{2\psi} & \cos{2\psi}
	\end{array}\right)
	\left(\begin{array}{cc}
		\frac{1}{2}\left(1+u^2\right) & 0 \\
		0 & u
	\end{array}\right) \nonumber\\\fl &\cdot&
	\left(\begin{array}{cc}
		\cos{2\phi_c} & -\sin{2\phi_c} \\
		\sin{2\phi_c} & \cos{2\phi_c}
	\end{array}\right)
	\left(\begin{array}{cc}
		1 \\
		i
	\end{array}\right) h(\omega; \boldsymbol\theta_\mathrm{in}).
\end{eqnarray}
%
This linear combination matches the conventions used in \cite{PhysRevD.83.084002}, and is the frequency-domain equivalent of their Equation~(2.8). The quantities $F_{+,i}$ and $F_{\times,i}$ are the dimensionless detector antenna factors, and depend on the orientation of detector $i$ as well as the sky location and sidereal time of the event, and are derived in~\cite{PhysRevD.63.042003}. The quantity $D_{1,i}$ is a fiducial distance at which detector $i$ would register SNR=1 for an optimally oriented binary (face\nobreakdashes-on, and in a direction perpendicular to the interferometer's arms),
%
\begin{equation}\label{eq:horizon}
D_{1,i} = 1 / \sigma_i, \qquad {\sigma_i}^2 = \int_0^\infty \frac{\left|h(\omega; \mathbf \theta)\right|^2}{S_i(\omega)} \,d\omega.
\end{equation}

@@

If we can show that the common factor approaches a delta function, $w(t; \rho) \rightarrow \delta(t)$ as $\rho \rightarrow \infty$, then the Fisher matrix approaches \Eref{eq:fisher-matrix} as $\rho \rightarrow \infty$. Certainly it behaves very much like a delta function. The Bessel functions asymptotically approach:
%
\begin{equation*}
	I_0(x), I_1(x) \rightarrow \frac{e^x}{\sqrt{2 \pi x}}
	\textrm{ as } x \rightarrow \infty.
\end{equation*}
%
For large $\rho$, it seems like we could write:
%
\begin{equation*}
	w(t; \rho) \rightarrow \frac{
		\displaystyle
		\exp\left[\frac{\rho^2}{2}|a(t)|^2\right]
	}{
		\displaystyle
		\int_{-\infty}^\infty \exp\left[\frac{\rho^2}{2}|a(t')|^2\right] dt'
	}
	\textrm{ as } \rho \rightarrow \infty.
\end{equation*}

>>>>

Assuming circular orbits and no spin precession, we can write the \ac{GW} signal in each detector as a linear combination of two basis waveforms $h_0$ = $h$ and $h_{\pi/2}$. For nonprecessing systems, $h_0$ and $h_{\pi/2}$ are approximately ``in quadrature'' in the same sense as the sine and cosine functions, being nearly orthogonal and out of phase by ${\pi/2}$ at all frequencies. If $h_0$ and $h_{\pi/2}$ are Fourier transforms of real functions, then $h_0(\omega) = h_0^*(-\omega)$ and $h_{\pi/2}(\omega) = h_{\pi/2}^*(-\omega)$, and we can write (assuming an arbitrary phase convention)
%
\begin{equation}
	h_{\pi/2}(\omega) = h_0(\omega) \cdot
	\cases{
		-i & if $\omega \geq 0$ \\
		i & if $\omega < 0$
	}.
\end{equation}
%
Then, we can write the signal model in a way that isolates all dependence on the extrinsic parameters $\boldsymbol\theta_\mathrm{ex}$ into the coefficients and all dependence on the intrinsic parameters $\boldsymbol\theta_\mathrm{in}$ into the basis waveform, by taking the Fourier transform of Equation~(2.8) of \cite{PhysRevD.83.084002}:
%
\begin{equation}\label{eq:full-signal-model}
	h_i(\omega; \boldsymbol\theta) = \e^{-i \omega t_\oplus}
	\frac{D_{1,i}}{D_\mathrm{L}}
	\e^{2 i \phi_c}
	\left[
	\frac{1}{2} \left(1 + \cos^2 \iota\right) \Re \left\{z\right\} - i
	\left(\cos\iota\right) \Im z
	\right]
	h(\omega; \boldsymbol\theta_\mathrm{in})
\end{equation}
%
for $\omega \geq 0$, where
%
\begin{equation}
	z = e^{-2 i \psi} \left(
	F_{+,i}(\alpha, \delta, t_\oplus) +
	i F_{\times,i}(\alpha, \delta, t_\oplus)
	\right).
\end{equation}
%
The quantities $F_{+,i}$ and $F_{\times,i}$ are the dimensionless detector antenna factors, and depend on the orientation of detector $i$ as well as the sky location and sidereal time of the event, and are derived in~\cite{PhysRevD.63.042003}. The quantity $D_{1,i}$ is a fiducial distance at which detector $i$ would register SNR=1 for an optimally oriented binary (face\nobreakdashes-on, and in a direction perpendicular to the interferometer's arms),
%
\marginpar{I seem to have dropped a factor of 2 here...}%
%
\begin{equation}\label{eq:horizon}
D_{1,i} = 1 / \sigma_i, \qquad {\sigma_i}^2 = \int_0^\infty \frac{\left|h(\omega; \mathbf \theta)\right|^2}{S_i(\omega)} \,d\omega.
\end{equation}

@@

Observe that
%
\begin{equation*}
	a(0) = 1,
	\qquad
	a'(0) = i \overline{\omega},
	\qquad
	a''(0) = -\overline{\omega^2}.
\end{equation*}
%
If we can show that the common factor approaches a delta function, $w(t; \rho) \rightarrow \delta(t)$ as $\rho \rightarrow \infty$, then the Fisher matrix approaches \Eref{eq:fisher-matrix} as $\rho \rightarrow \infty$. Certainly it behaves very much like a delta function. The Bessel functions asymptotically approach:
%
\begin{equation*}
	I_0(x), I_1(x) \rightarrow \frac{e^x}{\sqrt{2 \pi x}}
	\textrm{ as } x \rightarrow \infty.
\end{equation*}
%
For large $\rho$, it seems like we could write:
%
\begin{equation*}
	w(t; \rho) \rightarrow \frac{
		\displaystyle
		\exp\left[\frac{\rho^2}{2}|a(t)|^2\right]
	}{
		\displaystyle
		\int_{-\infty}^\infty \exp\left[\frac{\rho^2}{2}|a(t')|^2\right] dt'
	}
	\textrm{ as } \rho \rightarrow \infty.
\end{equation*}
